---
title: "AtividadeDeHoje"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is an example of Markdown vignettes in R. Before R 3.0.0, only Sweave/PDF vignettes were supported in R. Markdown is gaining popularity over the years due to its simplicity, and R 3.0.0 starts to support package vignettes written in R Markdown.


>Please note this example is for [R Markdown v1](https://rmarkdown.rstudio.com/authoring_migrating_from_v1.html) only. If you use [R Markdown v2](https://rmarkdown.rstudio.com/), you should use the vignette engine knitr::rmarkdown instead of knitr::knitr.


## Package vignettes

To enable Markdown vignettes in an R package, you need to

+ add *.Rmd files under the vignettes directory
+ add VignetteBuilder: knitr to the DESCRIPTION file
+ specify the vignette engine \VignetteEngine{knitr::knitr} in the Rmd files (inside HTML comments)


# View vignettes
And R will load the __knitr__ package to build these vignettes to HTML files, and you can see them when you open the HTML help:

```{r eval=FALSE, include=TRUE}
help(package = 'YourPackage', help_type = 'html')
# or see a standalone list of vignettes
browseVignettes('YourPackage')
```

# Examples
Below are some code chunks as examples.

```{r eval=FALSE}
if (TRUE) cat('_hello_ **markdown**!', '\n')
```

*hello* __markdown__! 

Normally you do not need any chunk options.

```{r eval=FALSE, include=TRUE}
1+1
## [1] 2
10:1
##  [1] 10  9  8  7  6  5  4  3  2  1
rnorm(5)^2
## [1] 0.008458 2.221310 3.826440 0.909318 0.285807
strsplit('hello, markdown vignettes', '')
## [[1]]
##  [1] "h" "e" "l" "l" "o" "," " " "m" "a" "r" "k" "d" "o" "w" "n" " " "v" "i" "g"
## [20] "n" "e" "t" "t" "e" "s"
```

Feel free to draw beautiful plots and write math $P(X>x)=alpha/2$

```{r plot, fig.height = 6, fig.width = 6, fig.align = "center"}
n=300; set.seed(123)
par(mar=c(4,4,.1,.1))
plot(rnorm(n), rnorm(n), pch=21, cex=5*runif(n), col='white', bg='gray')
```

You can use your own CSS file instead of the built-in style in the __markdown__ package – just set the option `markdown.HTML.stylesheet`, e.g.

```{r}
options(markdown.HTML.stylesheet = 'path/to/a/custom/style.css')
```
